Download data

### 2024-03-31 scripts/classify_patches.Rmd
working on fn to write out projects for senior botanists

lapply(files, FUN = landscapR, pout = 'patch_metrics', pRout = 'fine_patches')

@@

@@

f <- gsub('[.]tif$', '', list.files('../results/patches'))

# lentiformis  NTIF

lapply(f, combine_pop_patches) # 2:46
```

@@

@@

lapply(f, neigh_type)

>>>>

lapply(files[9:18], FUN = landscapR, pout = 'patch_metrics', pRout = 'fine_patches')
```

@@

# recs <- filter(recs, taxon %in% target_taxa)
# f <- f[grep(paste(paste0(gsub(' ', '_', target_taxa)), collapse = '|'), basename(f))]

@@

f <- gsub('[.]tif$', '', list.files('../results/patches'))
# f <- f[grep(paste(paste0(gsub(' ', '_', target_taxa)), collapse = '|'), basename(f))]

lapply(f, combine_pop_patches) 
```

@@

lapply(f, tif2shp)
```

@@

lapply(f, neigh_type)
```

### 2024-03-31 scripts/subsetDataforCrews.Rmd
working on fn to write out projects for senior botanists

```{r}
teams_list <- split(teams, f = teams$Contract)
```

@@

table(STZ$Dataset) 
head(STZ)
```

@@

p2ts <- '/media/steppe/hdd/SeedPhenology/data/processed/timestamps'
ott1 <- lapply(
  X = teams_list, # 5 throws an error
  FUN = phen_tabulator,
  path = p2ts, 
  admu = admin_boundaries, 
  target_species = spp_needed
  ) # row 67

>>>>

```{r}
teams_list <- split(teams, f = teams$Contract)
seniors_list <- split(seniors, f = seniors$Senior)
```

@@

lapply(seniors_list,  project_maker,
       admu = admin_boundaries, intype = 'senior',
       target_species = spp_needed, 
       blm_surf = blm_surf, 
       fs_surf = usfs_surf, 
       fire = fire_perimeters, 
       invasive = invasives, 
       total_change = change_intensity, 
       occurrences = occurrences, 
      # historic_SOS, 
       roads = roads, seed_transfer = STZ)

@@

p2ts <- '/media/steppe/hdd/SeedPhenology/data/processed/timestamps'
lapply(
  X = teams_list, # 5 throws an error
  FUN = phen_tabulator,
  path = p2ts, 
  admu = admin_boundaries, 
  target_species = spp_needed
  ) # row 67
